### 2018-02-13 thermoelectricity/paper.tex
stuff
everything except five and six

	Abstract goes here

@@

	The experimental setup included the TEC, \textbf{four} multimeters, current balance, Variac transformer, filter capacitors to filter out noise produced by the TEC, and a \textbf{thermometer}, all arranged as shown below.

@@

	To begin with, the temperatures of the input and output reservoirs and the ambient air were measured for several values of input power. To make the measurements, the terminals were open-circuited (obtained by unplugging one of the chords connecting the TEC to the DC ammeter). The ambient temperature was determined to be \( \pars{22.1 \pm 0.1} \si{\celsius} \), and was found to remain constant throughout the obtaining of the measurements.

@@

	Further, after allowing the system to cool off, the TEC was operated with an approximately fixed current supplied from the built-in power supply. The Variac transformer was turned off; measurements of voltage across the TEC and the current supplied to it, as well as the temperatures of the output and the input reservoir were taken.

@@

\end{papertable}\vspace{-0.5em}}{Measurements of $T_{out}$ ($\si{\celsius}$), $T_d$ ($\si{\celsius}$), $V_d$ ($\si{\volt}$), and $I_d$ ($\si{\ampere}$) for the first part of the second part of the experiment.}

	\paperfig{TableTwoBOne}{\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[inner]C|[outer]}\paperoline
			\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertablecheadersymbol{V_d~(\si{\volt})}\papertablecheadersymbol{I_d~(\si{\ampere})}\\
			\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertablecheaderunit{.004}{$\si{\volt}$}\papertablecheaderunit{.3}{$\si{\ampere}$}\\\paperiline
\papertableindex\papertablecval{27.9}\papertablecval{-7.0}\papertablecval{2.573}\papertablecval{12.1}\\\paperiline
\papertableindex\papertablecval{27.9}\papertablecval{-6.6}\papertablecval{2.603}\papertablecval{12.6}\\\paperiline
\papertableindex\papertablecval{28.0}\papertablecval{-5.3}\papertablecval{2.524}\papertablecval{12.4}\\\paperiline
\papertableindex\papertablecval{28.0}\papertablecval{-3.9}\papertablecval{2.535}\papertablecval{12.8}\\\paperiline
\papertableindex\papertablecval{28.0}\papertablecval{-2.7}\papertablecval{2.510}\papertablecval{12.8}\\\paperiline
\papertableindex\papertablecval{28.1}\papertablecval{-1.4}\papertablecval{2.479}\papertablecval{12.9}\\\paperiline
\papertableindex\papertablecval{28.9}\papertablecval{-0.3}\papertablecval{2.752}\papertablecval{14.8}\\\paperiline
\papertableindex\papertablecval{29.4}\papertablecval{0.4}\papertablecval{2.742}\papertablecval{15.0}\\\paperiline
\papertableindex\papertablecval{28.9}\papertablecval{2.2}\papertablecval{2.447}\papertablecval{13.6}\\\paperiline
\papertableindex\papertablecval{28.5}\papertablecval{4.0}\papertablecval{2.512}\papertablecval{14.3}\\\paperiline
\papertableindex\papertablecval{28.7}\papertablecval{5.4}\papertablecval{2.542}\papertablecval{14.8}\\\paperoline
	\end{papertable}\vspace{-0.5em}}{TODO}

	\paperfig{TableTwoBOne}{\centering\begin{papertable}{|[outer]I|[inner]U|[inner]U|[inner]C|[outer]}\paperoline
			\papertableindexheader\papertableuheadersymbol{V_{in}}\papertableuheadersymbol{I_{in}}\papertablecheadersymbol{V_s}\\
			\papertableuheadersymbol{(\si{\volt})}\papertableuheadersymbol{(\si{\ampere})}\papertablecheadersymbol{(\si{\volt})}\\\paperiline
\papertableindex\papertableuval{0.00}{.02}\papertableuval{0.00}{.01}\papertablecval{0.408}\\\paperiline
\papertableindex\papertableuval{0.67}{.03}\papertableuval{1.50}{.05}\papertablecval{0.396}\\\paperiline
\papertableindex\papertableuval{0.95}{.04}\papertableuval{2.12}{.06}\papertablecval{0.392}\\\paperiline
\papertableindex\papertableuval{1.16}{.04}\papertableuval{2.57}{.07}\papertablecval{0.367}\\\paperiline
\papertableindex\papertableuval{1.34}{.05}\papertableuval{2.99}{.08}\papertablecval{0.353}\\\paperiline
\papertableindex\papertableuval{1.50}{.05}\papertableuval{3.33}{.09}\papertablecval{0.336}\\\paperiline
\papertableindex\papertableuval{1.66}{.05}\papertableuval{3.6}{.1}\papertablecval{0.339}\\\paperiline
\papertableindex\papertableuval{1.78}{.06}\papertableuval{3.9}{.1}\papertablecval{0.337}\\\paperiline
\papertableindex\papertableuval{1.90}{.06}\papertableuval{4.2}{.1}\papertablecval{0.304}\\\paperiline
\papertableindex\papertableuval{2.03}{.06}\papertableuval{4.4}{.1}\papertablecval{0.281}\\\paperiline
\papertableindex\papertableuval{2.13}{.06}\papertableuval{4.7}{.1}\papertablecval{0.273}\\\paperoline
	\end{papertable}\vspace{-0.5em}}{TODO}

@@

	\paperfig{part1}{\pdf{1}}{Temperature difference plotted against the power for the open-circuited terminals. The error bars were included but were too small to be visible.}

@@

	\paperfig{part2a}{\pdf{part2a-data}}{Power and temperature difference plotted against time. Uncertainties were included but were too small to be visible.}

@@

	Conclusion goes here

>>>>

	This experiment investigated the properties of thermoelectric cooling. This
process is based on the Peltier and Seeback effects to use energy to pump heat.
This experiment measured various properties of the thermoelectric cooler.
The thermal conductance between the two reservoirs, $K_d$, was found to be $(0.59\pm.06)\si{\watt\per\kelvin}$.
The thermal conductance between the output heat sink and the ambient, $K_{hs}$, air was found to be $(7.1\pm.9)\si{\watt\per\kelvin}$.
The Seebeck coefficient for the system, $S_d$, was determined to be $(11.6\pm.1)\si{\milli\volt\per\kelvin}$.
The internal resistance of the thermoelectric cooler, $R_d$, was determined to be $(0.19\pm.01)\si{\ohm}$.
The lowest achievable temperature at the thermal reservoir with no heat input was determined to be $(-9.1\pm.2)\si{\kelvin}$.
The optimum drive current for the system was determined to be TODO.
The lowest achievable temperature with the optimum input current was determined to be TODO.

@@

	The experimental setup included the TEC, four multimeters, current balance, Variac transformer, filter capacitors to filter out noise produced by the TEC, and a temperature sensor, all arranged as shown below.

@@

	To begin with, the temperatures of the input and output reservoirs and the ambient air were measured for several values of input power. To make the measurements, the terminals were open-circuited (obtained by unplugging one of the chords connecting the TEC to the DC ammeter).

	The ambient temperature was determined to be \( \pars{22.1 \pm 0.1} \si{\celsius} \), and was found to remain constant throughout the obtaining of the measurements.

	The following are measured values of the temperatures of the input reservoir, the heat sink, the input potential and the input current.

@@

@@

\end{papertable}\vspace{-0.5em}}{Measurements of $T_{out}$ ($\si{\celsius}$), $T_{in}$ ($\si{\celsius}$), $V_d$ ($\si{\volt}$), and $I_d$ ($\si{\ampere}$) for the first part of the second part of the experiment.}

	Further, after allowing the system to cool off, the TEC was operated with an approximately fixed current supplied from the built-in power supply. The Variac transformer was turned off; measurements of voltage across the TEC and the current supplied to it, as well as the temperatures of the output and the input reservoir were taken (see \figPartTwoA).

	One of the main sources of error in the experiment was the non-constant potential of the current balance, which seemed to always be smaller than the marked potential of 6 volts. For this reason, a fourth multimeter was used in the data collection to account for this.

	\paperfig{TableTwoBOne}{\centering\begin{papertable}{|[outer]I|[inner]C|[inner]C|[inner]C|[inner]C|[outer]}\paperoline
			\papertableindexheader\papertablecheadersymbol{T_{out}}\papertablecheadersymbol{T_{in}}\papertablecheadersymbol{V_d~(\si{\volt})}\papertablecheadersymbol{I_d~(\si{\ampere})}\\
			\papertablecheadersymbol{\pm.1\degree}\papertablecheadersymbol{\pm.1\degree}\papertablecheaderunit{.004}{$\si{\volt}$}\papertablecheaderunit{.3}{$\si{\ampere}$}\\\paperiline
\papertableindex\papertablecval{27.9}\papertablecval{-7.0}\papertablecval{2.573}\papertablecval{12.1}\\\paperiline
\papertableindex\papertablecval{27.9}\papertablecval{-6.6}\papertablecval{2.603}\papertablecval{12.6}\\\paperiline
\papertableindex\papertablecval{28.0}\papertablecval{-5.3}\papertablecval{2.524}\papertablecval{12.4}\\\paperiline
\papertableindex\papertablecval{28.0}\papertablecval{-3.9}\papertablecval{2.535}\papertablecval{12.8}\\\paperiline
\papertableindex\papertablecval{28.0}\papertablecval{-2.7}\papertablecval{2.510}\papertablecval{12.8}\\\paperiline
\papertableindex\papertablecval{28.1}\papertablecval{-1.4}\papertablecval{2.479}\papertablecval{12.9}\\\paperiline
\papertableindex\papertablecval{28.9}\papertablecval{-0.3}\papertablecval{2.752}\papertablecval{14.8}\\\paperiline
\papertableindex\papertablecval{29.4}\papertablecval{0.4}\papertablecval{2.742}\papertablecval{15.0}\\\paperiline
\papertableindex\papertablecval{28.9}\papertablecval{2.2}\papertablecval{2.447}\papertablecval{13.6}\\\paperiline
\papertableindex\papertablecval{28.5}\papertablecval{4.0}\papertablecval{2.512}\papertablecval{14.3}\\\paperiline
\papertableindex\papertablecval{28.7}\papertablecval{5.4}\papertablecval{2.542}\papertablecval{14.8}\\\paperoline
	\end{papertable}\vspace{-0.5em}}{Measurements of $T_{out}$ ($\si{\celsius}$), $T_d$ ($\si{\celsius}$), $V_d$ ($\si{\volt}$), and $I_d$ ($\si{\ampere}$) for the second part of the second part of the experiment.}\vspace{2em}

	\paperfig{TableTwoBOne}{\centering\begin{papertable}{|[outer]I|[inner]U|[inner]U|[inner]C|[outer]}\paperoline
			\papertableindexheader\papertableuheadersymbol{V_{in}}\papertableuheadersymbol{I_{in}}\papertablecheadersymbol{V_s}\\
			\papertableuheadersymbol{(\si{\volt})}\papertableuheadersymbol{(\si{\ampere})}\papertablecheadersymbol{(\si{\volt})}\\\paperiline
\papertableindex\papertableuval{0.00}{.02}\papertableuval{0.00}{.01}\papertablecval{0.408}\\\paperiline
\papertableindex\papertableuval{0.67}{.03}\papertableuval{1.50}{.05}\papertablecval{0.396}\\\paperiline
\papertableindex\papertableuval{0.95}{.04}\papertableuval{2.12}{.06}\papertablecval{0.392}\\\paperiline
\papertableindex\papertableuval{1.16}{.04}\papertableuval{2.57}{.07}\papertablecval{0.367}\\\paperiline
\papertableindex\papertableuval{1.34}{.05}\papertableuval{2.99}{.08}\papertablecval{0.353}\\\paperiline
\papertableindex\papertableuval{1.50}{.05}\papertableuval{3.33}{.09}\papertablecval{0.336}\\\paperiline
\papertableindex\papertableuval{1.66}{.05}\papertableuval{3.6}{.1}\papertablecval{0.339}\\\paperiline
\papertableindex\papertableuval{1.78}{.06}\papertableuval{3.9}{.1}\papertablecval{0.337}\\\paperiline
\papertableindex\papertableuval{1.90}{.06}\papertableuval{4.2}{.1}\papertablecval{0.304}\\\paperiline
\papertableindex\papertableuval{2.03}{.06}\papertableuval{4.4}{.1}\papertablecval{0.281}\\\paperiline
\papertableindex\papertableuval{2.13}{.06}\papertableuval{4.7}{.1}\papertablecval{0.273}\\\paperoline
	\end{papertable}\vspace{-0.5em}}{Measurements of $V_{in}$ ($\si{\volt}$), $I_{in}$ ($\si{\ampere}$), and $V_s$ ($\si{\volt}$) for the second part of the second part of the experiment.}\vspace{2em}

@@

	\paperfig{PartOne}{\pdf{1}}{Temperature difference plotted against the power for the open-circuited terminals. The error bars were included but were too small to be visible. Linear functions were fitted to the two curves in the graph. The reciprocals of their slopes are the thermal conductances between the relevant materials. The thermal conductance between the two reservoirs, $K_d$, was found to be $(0.59\pm.06)\si{\watt\per\kelvin}$. This fit had a reduced $\chi^2$ of 24.2124 and an $R^2$ value of 0.962248. The thermal conductance between the output heat sink and the ambient, $K_{hs}$, air was found to be $(7.1\pm.9)\si{\watt\per\kelvin}$. This fit had a reduced $\chi^2$ of 0.307025 and an $R^2$ value of 0.933316.}

@@

	The thermal conductance between the input and the output reservoirs, $K_d$, obeys the following relation.

	\papereq{Kd}{P_K=K_d\Delta T}{AF, 2014}

	The thermal conductance between the output heat sink and the ambient air, $K_{hs}$, obeys a similar relation. Thus, the values of $K_d$ and $K_{hs}$ were computed by fitting linear functions to the curves in \figPartOne and taking the reciprocals of the obtained values. The thermal conductance between the two reservoirs, $K_d$, was found to be $(0.59\pm.06)\si{\watt\per\kelvin}$.
The thermal conductance between the output heat sink and the ambient, $K_{hs}$, air was found to be $(7.1\pm.9)\si{\watt\per\kelvin}$.

	\paperfig{partTwoa}{\pdf{part2a-data}}{Power and temperature difference plotted against time. Uncertainties were included but were too small to be visible. An increasing exponential function with a plateau was fit to the temperature difference. The plateau was determined to have a height of $(37.3\pm.2)\si{\kelvin}$. This fit had a reduced $\chi^2$ of 20.3006 and an $R^2$ value of 0.994558.}

	An overall linear increase in the power input as a function of time was observed except for the rapid decreases that could be attributed to noise in the circuit.

	The TEC model was used to predict the lowest achievable temperature with no heat input. This was done by modeling the graph in \figpartTwoa as an increasing exponential function with a plateau. This resulted in the largest possible temperature difference, which was compared against the existing data in \figPartTwoA. As a result, the lowest achievable temperature at the thermal reservoir with no heat input was determined to be $(-9.1\pm.2)\si{\kelvin}$.

@@

	Although most of the values obtained in this experiment had high precision, the experiment was not free from sources of error. The primary source of error was the fluctuating potential of the current balance. An attempt was made to mitigate this by adding a fourth multimeter to the data collection.

	A secondary source of error came from the fact that both the input thermal reservoir and the heat sink were both in contact with the surrounding air, in which eddies and other current were free to exchange heat, thereby introducing uncertainty into the measurements in this experiment.

	Aside from the sources of error, the experiment was successful in determining the key values in question. These were determined to be the following.
The thermal conductance between the two reservoirs, $K_d$, was found to be $(0.59\pm.06)\si{\watt\per\kelvin}$.
The thermal conductance between the output heat sink and the ambient, $K_{hs}$, air was found to be $(7.1\pm.9)\si{\watt\per\kelvin}$.
The Seebeck coefficient for the system, $S_d$, was determined to be $(11.6\pm.1)\si{\milli\volt\per\kelvin}$.
The internal resistance of the thermoelectric cooler, $R_d$, was determined to be $(0.19\pm.01)\si{\ohm}$.
The lowest achievable temperature at the thermal reservoir with no heat input was determined to be $(-9.1\pm.2)\si{\kelvin}$.
The optimum drive current for the system was determined to be TODO.
The lowest achievable temperature with the optimum input current was determined to be TODO.
